Quasi-Monte Carlo Methods: What, Why, and How?

### 2024-10-25 HickernellMCQMC2024_QMCTutorial.tex
txs auto checkin
M2 Mac updates

How one generates scenarios
%
\section{Where in Practice} \label{sec:practice}
\section{Low Discrepancy Sequence Constructions} \label{sec:construct}
\section{Discrepancy} \label{sec:discrepancy}
\section{Stopping Criteria} \label{sec:stop}
\section{Reformulating Our Problem} \label{sec:reformulate}
\section{Ongoing Research} \label{sec:onging}
\section{Conclusion} \label{sec:conclusion}

>>>>

Simple or independent and identically distributed (IID)  Monte Carlo chooses $\bsX_0, \bsX_1, \ldots$ to be IID.  Quasi-Monte Carlo (qMC) methods choose $\bsX_0, \bsX_1, \ldots$ \emph{not} IID, but to have an empirical distribution that is close to the actual probability distribution of $\bsX$.  The difference between these two distributions is called a \emph{discrepancy}, and the sequences used in qMC are called low discrepancy sequences.

This tutorial describes how

%
\section{Where in Practice} \label{sec:practice}
\section{Low Discrepancy Sequence Constructions} \label{sec:construct}
\section{Discrepancy} \label{sec:discrepancy}
\section{Stopping Criteria} \label{sec:stop}
\section{Reformulating Our Problem} \label{sec:reformulate}
\section{Ongoing Research} \label{sec:onging}
\section{Conclusion} \label{sec:conclusion}
